---
title: "Statistical Concepts"
author: "Moritz Seefeldt"
---

#Assignments
```{r}
#getwd()
random_vars <- readRDS("data/random_vars.rds")
#View(random_vars)

x1_mean <- mean(random_vars$age)
x1_var <- var(random_vars$age)
x1_sd <- sd(random_vars$age)

x2_mean <- mean(random_vars$income)
x2_var <- var(random_vars$income)
x2_sd <- sd(random_vars$income)

print(x1_mean)
print(x1_var)
print(x1_sd)

print(x2_mean)
print(x2_var)
print(x2_sd)

```
Comparing the standard deviations can make sense, as it is a measure of the spread (dispersion) of a random variable. In this case, the dispersion of the income is much larger than the dispersion of age, as would be expected.

```{r}
covariance <- cov(random_vars$age, random_vars$income)
correlation <- cor(random_vars$age, random_vars$income)

cat("Covariance: ", covariance, "\n")
cat("Correlation: ", correlation, "\n")
```
The correlation is easier to interpret as it is unit-less (between -1 and +1). A correlation of around 0.55 implies a positive, somewhat linear relationship between the two random variables.

```{r}
subset_minors <- subset(random_vars, age <= 18)
subset_adults <- subset(random_vars, age >= 18 & age <= 65)
subset_seniors <- subset(random_vars, age >= 65)

mean_minors <- mean(subset_minors$income)
mean_adults <- mean(subset_adults$income)
mean_seniors <- mean(subset_seniors$income)

print(mean_minors)
print(mean_adults)
print(mean_seniors)
```