---
title: "Regression and Statistical Inference"
author: "Moritz Seefeldt"
---

# Dimensions
```{r}
df <- readRDS("data/car_prices.rds")
cat("The dimensions are ", dim(df), "\n")
```

# Data types
```{r}
str(df)
```
There are two data types: Numbers ("num") and strings ("chr").

# Linear regression
```{r}
model <- lm(price ~., data = df)
summary(model)

min_rpm <- min(df$peakrpm)
max_rpm <- max(df$peakrpm)
```
# Regressor: peakrpm
The attribute "peakrpm" is of numeric type and can take on values between 4200 and 6600 (within the given dataset).
Peak RPM stands for the maximum revolutions per minute the car's engine will be able to perform.
Since the coefficient estimate is positive, the price of the var will increase as the value of "peakrpm" increases. 
The statistical significance is indicated by the p-value: A small p-value implies a high statistical significance. Since the p-value is rather small for the chosen attribute (0.000108), it is of high statistical significance.

# Seat heating
```{r}
library(dplyr)

df <- df %>%
  mutate(seat_heating = TRUE)

summary(df)

model <- lm(price ~., data = df)
summary(model)
```
The output results in an error, since the model matrix will be singular (all values are the same; "TRUE") and have no inverse. It obviously would not have any impact on the price either, since it is constant across the entire dataset.