---
title: "Directed Acyclic Graphs"
author: "Moritz Seefeldt"
---

# Assignment 1
```{r}
# Confounder
confounding <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "Parking spot available",
                Y = "Sales",
                Z = "Customers")
)

# Plot DAG
ggdag(confounding) +
  #geom_dag_point(color = ggthemr::swatch()[2]) +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "white") +
  geom_dag_label_repel(aes(label = label))
```
# Assignment 2
```{r}
df <- readRDS("data/customer_sat.rds")
str(df)
df

model1 <- lm(satisfaction ~ follow_ups, data = df)
summary(model1)

model2 <- lm(satisfaction ~ follow_ups + subscription, data = df)
summary(model2)
```
# Assignment 3
The estimated coefficient for the number of follow-up calls is negative, meaning the satisfaction is expected to decrease if the customer receives more calls. However, this appears to originate from the connection between the number of follow-up calls and the subscription model.

The estimated coefficient for the number of follow-up calls while accounting for the subscription model is positive, meaning that the satisfaction is expected to increase with the number of calls while within a given subscription model.

This could be indicative of the fact that the customer might be experiencing more issues and problems with the software for more expensive subscription models (while also having higher expectations?). 
The data still suggests that making more follow-up calls will result in a higher customer satisfaction.

# Assignment 4

```{r}

satisfaction_not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point() +
  stat_smooth(method = "lm", se = F)

# Conditioning on student  
satisfaction_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction,
                            color = subscription, 
                            alpha = subscription)) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  scale_color_manual(values = c("Elite" = "red",
                                "Premium+" = "blue",
                                "Premium" = "green")) +
  scale_alpha_manual(values = c("Elite" = 1, "Premium+" = 0.6, "Premium" = 0.2)) +
  theme(legend.position = "right")


satisfaction_not_cond
satisfaction_cond
```
